\chapter{Future work}

Currently is being developed many features for future use or are intended to being used. Here are presented a small list of them:
\begin{itemize}
    \tightlist
    \item Finish the VIENA interface webpage
    \item Implement security layers for MQTT (SSL, TLS).
    \item Add login for MQTT to avoid possible intrusions.
    \item Acquire the designed \gls{PCB} board to replace the CAN protoboard.
    \item Design python module to control both power train and steering wheel  using the common CAN bus.
    \item Design and implement \gls{BMS} for pack of auxiliary batteries.
    \item Design and implement a structure for fixing auxiliary batteries with easy access to connect a charger.
    \item Redesign code for new \gls{AHRS} sensors.
    \item Implement Location fusion based in \gls{GNSS}/\gls{AHRS} filter in python.
    \item Implement high level steering controller based on information received from Location filter information (with \gls{MQTT} access for now).
    \item Study the possibility of use of ROS2 in \gls{Rpi} for adding flexibility and abstraction.
    \item Add flexibility to safe shutdown \gls{Rpi} using a pushbutton or switch to avoid damaging microSD cards.
    \item Study the possibility to change root (or full boot) partition to USB or mSSD solutions.
    \item Create robust fixture structure to accommodate all boards and sensors currently used.
    \item Create 3D print enclosures for all circuits that can be easy installed/removed.
    \item Study the circuit required to auto-shutdown if pre-charge have any failure (possibly using high voltage LEM transducers)
    \item Create a full online documentation possibly based on Github project wiki that adds flexibility.
    \item Create a Github pages associated with project.
    \item Create a modular structure to fix components on the back of the vehicle, possibly based on open beam or Bosch Rexroth V slots.
\end{itemize}